---
title: "Aggregating Sequence Scores Results"
author: "hector@ciml.univ-mrs.fr"
output:
  html_document:
    code_folding: hide
    theme: cerulean
    toc: true
    toc_float: true
    mathjax: null 
    self_contained: true  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE,progress = FALSE, verbose = FALSE)
```



# Loading libraries and data 


```{r loadings}

#libraries
source( file.path( WORKING_DIR, "00_generalDeps.R"));
#source( file.path( WORKING_DIR, "allFunctions.R"));


# Data 
#"Input_table = "/mnt/DOSI/PMLAB/BIOINFO/FL_modeling/01_FL_vs_Physio_data_analysis/05_Output/04_Analysis/04_Merging_Results/MOUSE_GC_PMLAB/All_Samples_Merged_Scores.txt"

All_Scores_Df  = read.table(ALL_SCORES_TABLE, header = T)
All_Scores_Df = All_Scores_Df %>% dplyr::mutate(Clone_Size =   as.numeric(gsub(".*CLONOTYPE_n(.+)_Id.*", "\\1", Clonotype))  )


All_Clones_Df = read.table(ALL_CLONES_TABLE, header = T, sep = "\t")
if("Sample" %in% names(All_Clones_Df) ==F){All_Clones_Df$Sample = "All"}
#All_Clones_Df = as.data.frame(All_Clones_Df) %>% dplyr::select(cell_id, Sample, cloneID,  heavy_v_call,  light_v_call)

```



```{r}
read_chunk( path=file.path( WORKING_DIR, "01_CloneSize_Correlation.R"));
read_chunk( path=file.path( WORKING_DIR, "02_SelectScores_groups.R"));
read_chunk( path=file.path( WORKING_DIR, "03_Clonal_Diversity.R"));
```


# Clonal Diversity

```{r Clonal_Diversity, fig.width=7}
<<Clonal_Diversity>>

```

Chao1 is a non-parametric estimator widely used in studies of species richness in natural ecosystems. The rationale
is that if many species (or clones) are detected only once, there is likely a large number of
clones that have not yet been detected; when all clones have been detected at least twice,
it is unlikely that new undetected clones exist.
reference: https://www.uvm.edu/~ngotelli/manuscriptpdfs/Chapter%204.pdf 



```{r Chao1_Inference, fig.height=3}
<<Chao1_Inference>>

```


# Clone size vs Select Score 

```{r CloneSize_Correlation , fig.height=3.5, fig.width=5.5}
<<CloneSize_Correlation>>

```
<br />

# Select Score per group {.tabset .tabset-fade} 





```{r SelectScores_groups, fig.height=5.5, fig.width=11}
<<SelectScores_groups>>
```






<!-- Ending the tabset section -->
### {.toc-ignore} 
<br /><br />



# End


