---
title: "Aggregating Sequence Scores Results"
author: "hector@ciml.univ-mrs.fr"
output:
  html_document:
    code_folding: hide
    theme: cerulean
    toc: true
    toc_float: true
    mathjax: null 
    self_contained: true  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE,progress = FALSE, verbose = FALSE)
```



# Loading libraries and data 


```{r loadings}

#libraries
source( file.path( WORKING_DIR, "00_generalDeps.R"));
#source( file.path( WORKING_DIR, "allFunctions.R"));


# Data 
All_Scores_Df  = read.table(ALL_SCORES_TABLE, header = T, row.names = NULL)

All_Scores_Df_Repeated_Seqs = All_Scores_Df
All_Scores_Df = distinct(All_Scores_Df %>% dplyr::select(-SeqID))  

All_Scores_Df = All_Scores_Df %>% dplyr::mutate(Clone_Size =   as.numeric(gsub(".*CLONOTYPE_n(.+)_Id.*", "\\1", Clonotype))    ) %>% dplyr::filter(Dist_ToGermline < 75 )
						 #Global_Select_Score = as.numeric(Global_Select_Score), Cumulated_Select_Score = as.numeric(Cumulated_Select_Score)  )


All_Clones_Df = read.table(ALL_CLONES_TABLE, header = T) #, sep = "\t"
if("Sample" %in% names(All_Clones_Df) ==F){All_Clones_Df$Sample = "All"}


```



```{r}
read_chunk( path=file.path( WORKING_DIR, "01_CloneSize_Correlation.R"));
read_chunk( path=file.path( WORKING_DIR, "02_SelectScores_groups.R"));
read_chunk( path=file.path( WORKING_DIR, "03_Clonal_Diversity.R"));
read_chunk( path=file.path( WORKING_DIR, "04_AA_properties.R"));
read_chunk( path=file.path( WORKING_DIR, "05_Updating_Metadata.R"));

```


# Clonal Diversity

```{r Clonal_Diversity, fig.width=7}
<<Clonal_Diversity>>

```

Chao1 is a non-parametric estimator widely used in studies of species richness in natural ecosystems. The rationale
is that if many species (or clones) are detected only once, there is likely a large number of
clones that have not yet been detected; when all clones have been detected at least twice,
it is unlikely that new undetected clones exist.
reference: https://www.uvm.edu/~ngotelli/manuscriptpdfs/Chapter%204.pdf 



```{r Chao1_Inference, fig.height=3}
<<Chao1_Inference>>

```


# Clone size vs Select Score 
```{r}
#All_Scores_Df = All_Scores_Df %>% dplyr::filter( as.numeric(Global_Select_Score) < 0.9 ) #TO DELETE AFTER? TEMPORARY SOLUTION 
#Selecting sequences that are closely related to real sequence (no gaps + no inferrence)
#All_Scores_Df = All_Scores_Df %>% dplyr::filter( as.numeric(MutSinceParent) <4  ) #& grepl("[Ss]eq", ParentNode )
```



```{r CloneSize_Correlation , fig.height=3.5, fig.width=5.5}
<<CloneSize_Correlation>>

```
<br />

# Select Score per group 




# Cells Groups comparison {.tabset .tabset-fade}

```{r SelectScores_groups, fig.height=5, fig.width=11, results = "asis"}
<<SelectScores_groups>>
```






<!-- Ending the tabset section -->
### {.toc-ignore} 
<br /><br />



# Mutation Patterns {.tabset .tabset-fade}

```{r AA_properties, results = "asis"}
<<AA_properties>>
```



# Updating Metadata

#```{r updateMetadata}
#<<updateMetadata>>
#```


